Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield

### 2017-09-04 Tex/Paper.tex
Added beam emittance scan figure

We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated
and minimize the emittance growth. In addition, the bunch length should be such that it is possible to generate and
transport by a compact electron injector [IPAC]. These are contradictory constraints. We  investigate the
interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial emittance. We
quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will depend
on the application.

@@

@@

% ******************************************************************************************************************** %
\section[\label{S:D}]{Discussion}
% discussion of optimal electron beam parameters
% implications for AWAKE Run 2
% ******************************************************************************************************************** %

>>>>

We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated
and minimize the emittance growth. In addition, the bunch length should be such that it is possible to generate and
transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We  investigate the
interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial emittance. We
quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will depend
on the application.

@@

\begin{figure}[hbt]
    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
    \caption{\label{Fig:BeamQEmit} }
\end{figure}

@@
